Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-02 overleaf/introduction.tex
Edits to shorten.

Earlier compilers did both back-end and front-end translation as their aim was to demonstrate applicability of MPC on real-world
programming problems. As the field advanced, works have focused more closely on front-end language design (e.g., Wysteria~\cite{SP:RasHamHic14} and Viaduct~\cite{Acay:2021})
or back-end ``circuit-level'' design and implementation (e.g., MOTION~\cite{Braun:2022}).

@@

We formalize the MPC Source~\cite{Ishaq:2019} intermediate representation and emphasize optimization over MPC Source. As in classical compilers, we envision different front ends (e.g., our front end IMP Source, other) compiling into MPC Source. MPC Source is particularly suitable for optimizations such as protocol mixing~\cite{Ishaq:2019, Fang:2022} and SIMD-vectorization,
which takes advantage of amortization at the circuit level. The MPC Source IR exposes the \emph{linear structure} of MPC programs, which simplifies program analysis; this is
in contrast to source, which has if-then-else constructs. In the same time, MPC Source is sufficiently ``high-level''  to support analysis and optimizations that take into account
control and data flow in a specific program. MPC Source facilitates cost modeling. 
%MPC Source is small in size and analysis is tractable, as opposed to analysis over an unrolled circuit~\cite{Ishaq:2019}. 
Again as in classical compilers, we envision translation of MPC Source (optimized or unoptimized) into MOTION, SPDZ, or other back-end code.

@@

\subsection{Our Contribution} In this paper, we develop a compiler framework that takes a Python-like routine and produces MOTION code: we describe (a) the IMP Source language, its syntax and semantic restrictions, (b) translation from IMP Source into MPC Source, (c) a specific backend-independent optimization: novel SIMD-vectorization on MPC Source, and (d) translation from MPC Source into MOTION code. %\ana{I think we have to add more on MOTION, specifically mixing and amortization.}

We focus on the MOTION framework as our back-end for several reasons. First, it is the state of the art in terms of performance~\cite{Braun:2022}. Second, it provides an API over efficient implementation for a wide variety of cryptographic operations in three different protocols ---  Arithmetic GMW, Boolean GMW, and BMR --- which allows for protocol mixing~\cite{Ishaq:2019, Fang:2022}, a known backend-independent optimization. Third, MOTION provides API for SIMD-level operations, which amortize cost and lead to significant improvement in memory footprint and
throughput~\cite{NDSS:DemSchZoh15, CCS:ABFKLO18, Braun:2022}. It enables MPC Source-level vectorization, a key focus of this paper.

Our second contribution is an analytical model for cost estimation of amortized schedules. Originally, we hoped that optimal scheduling (under our model, which essentially minimizes the length of the schedule) was tractable, as the problem appeared simpler than the classical scheduling problem. Unfortunately, we show that optimal scheduling is NP-hard via a reduction to the Shortest Common Supersequence (SCS) problem. Cost modeling is important as it drives not only vectorization but optimizations such as protocol mixing and scheduling as well~\cite{Ishaq:2019, Fang:2022}.

Our most important contribution is the implementation and evaluation of the compiler framework. We demonstrate expressivity of the source language by running the compiler on \ana{X} programs with interleaved if- and for-statements; these include classical MPC benchmarks such as PSI and Biometric matching, as well as kMeans, Histogram, and others. \ana{Summarize results.}

@@

>>>>

%Earlier compilers did both back-end and front-end translation as their aim was to demonstrate applicability of MPC on real-world
%programming problems. As the field advanced, works have focused more closely on front-end language design (e.g., Wysteria~\cite{SP:RasHamHic14} and Viaduct~\cite{Acay:2021})
%or back-end ``circuit-level'' design and implementation (e.g., MOTION~\cite{Braun:2022}).

@@

We formalize the MPC Source~\cite{Ishaq:2019} intermediate representation and emphasize optimization over MPC Source. As in classical compilers, we envision different front ends (e.g., our front end IMP Source) compiling into MPC Source. MPC Source is particularly suitable for optimizations such as protocol mixing~\cite{CCS:BDKKS18,Ishaq:2019, Fang:2022} and SIMD-vectorization,
which takes advantage of amortization at the circuit level. The MPC Source IR exposes the \emph{linear structure} of MPC programs, which simplifies program analysis; this is
in contrast to source, which has if-then-else constructs. In the same time, MPC Source is sufficiently ``high-level''  to support analysis and optimizations that take into account
control and data flow in a specific program. %MPC Source facilitates cost modeling. 
%MPC Source is small in size and analysis is tractable, as opposed to analysis over an unrolled circuit~\cite{Ishaq:2019}. 
Again as in classical compilers, we envision translation of MPC Source (optimized or unoptimized) into MOTION, SPDZ, or other back-end code.

@@

\subsection{Our Contribution} In this paper, we develop a compiler framework that takes a Python-like routine and produces MOTION code: we describe (a) the IMP Source language, its syntax and semantic restrictions, (b) translation into MPC Source, (c) a specific backend-independent optimization: novel SIMD-vectorization on MPC Source, and (d) translation from MPC Source into MOTION code. %\ana{I think we have to add more on MOTION, specifically mixing and amortization.}

We focus on the MOTION framework as our back-end for several reasons. First, it demonstrates high performance~\cite{Braun:2022}. Second, it provides an API over efficient implementation for a wide variety of cryptographic operations (e.g., MUL, CMP, etc.) in three different protocols ---  Arithmetic GMW, Boolean GMW, and BMR --- which allows for protocol mixing~\cite{CCS:BDKKS18,Ishaq:2019, Fang:2022}, a known backend-independent optimization. Third, MOTION provides API for SIMD-level operations (e.g., MUL\_SIMD), which amortize cost and lead to significant improvement in memory footprint and throughput~\cite{NDSS:DemSchZoh15, CCS:ABFKLO18, Braun:2022}. It enables MPC Source-level vectorization, a key focus of this paper.

Our second contribution is an analytical model for cost estimation of amortized schedules. Originally, we hoped that optimal scheduling (under our model, which essentially minimizes the length of the schedule) was tractable, as the problem appeared simpler than the classical scheduling problem. Unfortunately, we show that optimal scheduling is NP-hard via a reduction to the Shortest Common Supersequence (SCS) problem. Cost modeling is important as it drives not only vectorization but optimizations such as protocol mixing and scheduling as well~\cite{CCS:BDKKS18,Ishaq:2019, Fang:2022}.

Our most important contribution is the implementation and evaluation of the compiler framework. We demonstrate expressivity of the source language by running the compiler on 16 programs with interleaved if- and for-statements; these include classical MPC benchmarks such as PSI and Biometric matching, as well as kMeans, Histogram, and other examples from the literature. 
Our compiler takes the routine and generated \emph{non-vectorized} MOTION code (from MPC Source on the picture above). It then optimizes MPC Source and generates 
\emph{vectorized} MOTION code (from Optimized MPC Source). We then run the two versions using Boolean GMW and the BMR protocols. (MOTION, which is designed for 
protocol mixing, supports Arithmetic GMW, however, it does not implement Comparison (CMP) and Multiplexing (MUX) as they would be rather inefficient.)
In our experiments vectorized code exhibits 24x improvement on average in circuit generation time for Boolean GMW (20x for BMR), 7x reduction 
in communication (2x), 97x reduction in number of gates (91x), 4x improvement in setup time (23x) and 21x improvement in online time (18x).
%\ana{Summarize results.}

@@

All our code, including benchmark Python-like code, compilation phases, and generated MOTION code is available on Github. We omit the link for anonymity, 
however, we will gladly make it available upon request from reviewers. The Github setup generates graphs and intermediate code for each program along each compiler phase, compiles with 
MOTION and runs the circuits on small inputs to generate tables of data (the experiments we present later run on real LAN and WAN). We plan to release the link and code, which we believe will be useful to researchers.

### 2022-05-02 overleaf/model.tex
Edits to shorten.

\begin{enumerate}
\item All statements in the program execute using the same protocol (sharing). That is, there is no share conversion.
%\ishaq{This is not an assumption, this is our setting. We work in the single protocol world.}
\item There are two tiers of MPC instructions, local and remote. A local instruction (e.g., ADD in Arithmetic, XOR in Boolean) 
has cost $\beta$ and a remote instruction (e.g., MUX, MUL, SHL, etc.) has cost $\alpha$, where $\alpha >> \beta$. We assume that all remote
instructions have the same cost.
%\ishaq{Don't we need to distinguish between local (cheap) vs. interactive (expensive) instructions? I don't see how we could assume this. -- Past suggestion from Vassilis: Ideally we should assume cost to be a convex function.}\ana{After discussion 1/12: replace single costs 1 with two levels of costs: $\alpha$ for non-local operations, e.g., MUL, and $\beta$ for local ops, e.g., ADD.}
\item  In MPC frameworks, executing $n$ operations ``at once'' in a single SIMD operation costs a lot less than executing those $n$ operations one by one.
Following Amdahl's law, we write $\alpha = \frac{1}{s}p\alpha + (1-p)\alpha$, where $p$ is the fraction of execution time that benefits from amortization and $(1-p)$
is the fraction that does not, and $s$ is the available resource. Thus, $n\alpha = \frac{n}{s}p\alpha + n(1-p)\alpha$.
For the purpose of the model we assume that $s$ is large enough and the term $\frac{n}{s}p\alpha$ amounts to a \emph{fixed cost} incurred regardless of
whether $n$ is $10,000$ or just $1$. (This models the cost of preparing and sending a packet from party A to party B for example.) Therefore, amortized execution
of $n$ operations is $f(n) = \alpha_\mathit{fix} + n\alpha_{var}$ in contrast to unamortized execution $g(n) = n\alpha_\mathit{fix} + n\alpha_{var}$.
We have $\alpha_\mathit{fix} << n\alpha_\mathit{fix}$ and since fixed cost dominates variable cost (particularly for remote operations), we have $f(n) << g(n)$.
%We assume infinite parallel capacity---i.e., a single MPC-instruction costs as much as $N$ amortized instructions, namely $\alpha$ or $\beta$.
%This is a standard assumption in Cryptographic Parallel RAM. ABY presents empirical support for this assumption~\ana{Add citations. PRAM, ABY.}
%\ishaq{Comment from Vassilis: We assume there are infinite parallel capacities, this is the standard assumption in PRAM (Cryptographic Parallel RAM).}\ana{PRAM assumption stays. We have to replace the unit cost of 1 with a suitable amortization function $f(n)$, which I don't think changes much in the cost modeling and analysis.}
\item MPC instructions scheduled in parallel benefit from amortization \emph{only if} they are the same instruction. Given our previous assumption,
2 MUL instructions can be amortized in a single SIMD instruction that costs $\alpha_\mathit{fix} + 2\alpha_\mathit{var}$, however a MUL and a MUX instruction
still cost $2\alpha_\mathit{fix} + 2\alpha_\mathit{var}$ even when scheduled ``in parallel''.\footnote{This is not strictly true, but assuming it, e.g. as in 
\cite{Ishaq:2019, NDSS:DemSchZoh15, Mohassel:2018}, helps simplify the problem.}
%MPC instructions scheduled in parallel benefit from amortization \emph{only if} they are the same instruction. Given our previous assumption,
%2 MUL instructions scheduled in parallel benefit from amortization and cost $\alpha$, however a MUL and a MUX instructions scheduled
%in parallel still cost $2\alpha$.
%\ishaq{We need to reword this assumption to something like "$K$ parallel MUL costs much less than $K$ (because they get amortized), but any mix of $K$  MUL and MUX still cost roughly $K$. Specifically, we should take away the low constants (2 and 1) because we know for low constants this is not true.} \ana{Again, core assumption that MUL and MUX don't benefit from amortization stays. We have to replace constant costs with functions, as in (3).}
\end{enumerate}

>>>>

\begin{enumerate}

\item All statements in the program execute using the same protocol (sharing). That is, there is no share conversion.
%\ishaq{This is not an assumption, this is our setting. We work in the single protocol world.}
\item There are two tiers of MPC instructions, local and remote. A local instruction (e.g., ADD in Arithmetic, XOR in Boolean) 
has cost $\beta$ and a remote instruction (e.g., MUX, MUL, SHL, etc.) has cost $\alpha$, where $\alpha >> \beta$. We assume that all remote
instructions have the same cost.
%\ishaq{Don't we need to distinguish between local (cheap) vs. interactive (expensive) instructions? I don't see how we could assume this. -- Past suggestion from Vassilis: Ideally we should assume cost to be a convex function.}\ana{After discussion 1/12: replace single costs 1 with two levels of costs: $\alpha$ for non-local operations, e.g., MUL, and $\beta$ for local ops, e.g., ADD.}
\item  %In MPC frameworks, executing $n$ operations ``at once'' in a single SIMD operation costs a lot less than executing those $n$ operations one by one.
Following Amdahl's law, we write $\alpha = \frac{1}{s}p\alpha + (1-p)\alpha$, where $p$ is the fraction of execution time that benefits from amortization and $(1-p)$
is the fraction that does not, and $s$ is the available resource. Thus, $n\alpha = \frac{n}{s}p\alpha + n(1-p)\alpha$.
For the purpose of the model we assume that $s$ is large enough and the term $\frac{n}{s}p\alpha$ amounts to a \emph{fixed cost} incurred regardless of
whether $n$ is $10,000$ or just $1$. (This models the cost of preparing and sending a packet from party A to party B for example.) Therefore, amortized execution
of $n$ operations is $f(n) = \alpha_\mathit{fix} + n\alpha_{var}$ in contrast to unamortized execution $g(n) = n\alpha_\mathit{fix} + n\alpha_{var}$.
We have $\alpha_\mathit{fix} << n\alpha_\mathit{fix}$ and since fixed cost dominates variable cost (particularly for remote operations), we have $f(n) << g(n)$.
%We assume infinite parallel capacity---i.e., a single MPC-instruction costs as much as $N$ amortized instructions, namely $\alpha$ or $\beta$.
%This is a standard assumption in Cryptographic Parallel RAM. ABY presents empirical support for this assumption~\ana{Add citations. PRAM, ABY.}
%\ishaq{Comment from Vassilis: We assume there are infinite parallel capacities, this is the standard assumption in PRAM (Cryptographic Parallel RAM).}\ana{PRAM assumption stays. We have to replace the unit cost of 1 with a suitable amortization function $f(n)$, which I don't think changes much in the cost modeling and analysis.}
\item MPC instructions scheduled in parallel benefit from amortization \emph{only if} they are the same instruction. Given our previous assumption,
2 MUL instructions can be amortized in a single SIMD instruction that costs $\alpha_\mathit{fix} + 2\alpha_\mathit{var}$, however a MUL and a MUX instruction
still cost $2\alpha_\mathit{fix} + 2\alpha_\mathit{var}$ even when scheduled ``in parallel''.\footnote{This is not strictly true, but assuming it, e.g. as in 
\cite{Ishaq:2019, NDSS:DemSchZoh15, Mohassel:2018}, helps simplify the problem.}
%MPC instructions scheduled in parallel benefit from amortization \emph{only if} they are the same instruction. Given our previous assumption,
%2 MUL instructions scheduled in parallel benefit from amortization and cost $\alpha$, however a MUL and a MUX instructions scheduled
%in parallel still cost $2\alpha$.
%\ishaq{We need to reword this assumption to something like "$K$ parallel MUL costs much less than $K$ (because they get amortized), but any mix of $K$  MUL and MUX still cost roughly $K$. Specifically, we should take away the low constants (2 and 1) because we know for low constants this is not true.} \ana{Again, core assumption that MUL and MUX don't benefit from amortization stays. We have to replace constant costs with functions, as in (3).}
\end{enumerate}

### 2022-05-02 overleaf/overview.tex
Edits to shorten.

Our compiler takes essentially standard IMP~\ana{Need citation here.}
syntax and imposes certain semantic restrictions. (We detail the restrictions in the following sections.)
The programmer writes an iterative program and annotates certain inputs
and outputs as \emph{shared}. In the example arrays {\sf C} and {\sf S}
are \texttt{shared}, meaning that they store shares, however, the array sizes {\sf D} and
{\sf N} respectively are plaintext. The code iterates over the entries in the
database and computes the Euclidean distance of the current
entry ${\sf S}[i]$ and {\sf C} (its square actually). The program returns the index of the vector that gives
the best match plus the corresponding sum of squares.

@@

We turn to our analytical model to compute the \emph{cost} of the iterative program. Assuming
cost $\beta$ for a local MPC operation (essentially just ADD) and cost $\alpha$ for a remote
MPC operation (e.g., MUX, CMP, and remaining operations), the cost of the iterative schedule
will be $ND(2\alpha+\beta) + N(3\alpha$).

A key contribution is the vectorizing transformation. We can compute all $N*D$
subtraction operations (line 9 in (b)) in a single SIMD instruction; similarly we can compute
all multiplication operations (line 10) in a single SIMD instruction. And while computation
of an individual sum remains sequential, we can compute the $N$ sums in parallel.
Our compiler \emph{automatically detects these opportunities and transforms the program}.
It is standard that MPC researchers write vectorized versions of the Biometric
program by hand; we are the first (to the best of our knowledge) to automatically
transform a naive, iterative MPC program into an unintuitive vectorized one.

@@

In MPC back ends, executing $n$ operations ``at once'' in a single SIMD operation costs a lot less than executing those $n$ operations one by one.
This is particularly important when there is communication (i.e., in remote), since many 1-bit values are sent at once rather than sequentially.
%In MPC compilers a vectorized operation that computing M operations "at once" costs
%essentially the same ($\alpha$ or $\beta$) as an individual operation.
We elaborate on the cost model in Section~\secref{sec:model} but for now consider that
each operation has a \emph{fixed} portion (does benefits from amortization) and
a \emph{variable} portion (does not benefit from amortization): $\alpha = \alpha_\mathit{fix} + \alpha_\mathit{var}$.
This gives rise to the following formula for amortized cost: $f(n) = \alpha_\mathit{fix} + n\alpha_\mathit{var}$,
as opposed to unamortized cost $g(n) = n\alpha_\mathit{fix} + n\alpha_\mathit{var}$. (We extend the same reasoning to
$\beta$-instructions.)

Thus, the fixed cost of the vectorized program amounts to
$2\alpha_\mathit{fix}$ + $D \beta_\mathit{fix} + N(3\alpha_\mathit{fix})$. (The variable cost is the same in both the vectorized and non-vectorized programs.)
The first term in the sum corresponds to the vectorized
subtraction and multiplication (lines 9-10 in (c)), the second term corresponds to the for-loop on $j$ (lines 12-16) and the third
one corresponds to the remaining for-loops on $i$ (lines 19-25). 
Clearly, $2\alpha_\mathit{fix} + D\beta_\mathit{fix} + N(3\alpha_\mathit{fix}) << ND(2\alpha_\mathit{fix}+\beta_\mathit{fix}) + N3\alpha_\mathit{fix}$.
Empirically, we observe 10x to 50x improvement over un-vectorized Biometric Matching in circuit generation time and setup time and 5x to 30x improvement in online time.
Additionally, the un-vectorized version runs out of memory for $N=256$, while the vectorized one runs with the standard maximal input size $N=4,096$.
\ana{Edit numbers with final experiments.}

>>>>

Our compiler takes essentially standard IMP~\cite{Nipkow2014}
syntax and imposes certain semantic restrictions. %(We detail the restrictions in the following sections.)
The programmer writes an iterative program and annotates certain inputs
and outputs as \emph{shared}. In the example arrays {\sf C} and {\sf S}
are \texttt{shared}, meaning that they store shares, however, the array sizes {\sf D} and
{\sf N} respectively are plaintext. 
%The code iterates over the entries in the
%database and computes the Euclidean distance of the current
%entry ${\sf S}[i]$ and {\sf C} (its square actually). The program returns the index of the vector that gives
%the best match plus the corresponding sum of squares.

@@

We turn to our analytical model to compute the \emph{cost} of the iterative program. Assume
cost $\beta$ for a local MPC operation (e.g., ADD in Arithmetic sharing) and cost $\alpha$ for a remote
MPC operation (e.g., MUX, CMP, etc.). Assuming that ADD is $\beta$ and SUB, CMP and MUX are $\alpha$, 
the MPC Source in Listing~\ref{tab:source_and_MPC_source_and_optimized_MPC_source}(b) gives 
rise to an iterative schedule with cost $ND(2\alpha+\beta) + N(3\alpha$).

A key contribution is the vectorizing transformation. We can compute all $N*D$
subtractions (line 9 in (b)) in a single SIMD instruction; similarly we can compute
all multiplications (line 10) in a single SIMD instruction. And while computation
of an individual sum remains sequential, we can compute the $N$ sums in parallel.
%Our compiler \emph{automatically detects these opportunities and transforms the program}.
%It is standard that MPC researchers write vectorized versions of the Biometric
%program by hand; we are the first (to the best of our knowledge) to automatically
%transform a naive, iterative MPC program into an unintuitive vectorized one.

@@

In MPC back ends, executing $n$ operations ``at once'' in a single SIMD operation costs a lot less than executing those $n$ operations one by one.
This is particularly important when there is communication (i.e., in remote), since many 1-bit values are sent at once rather than sequentially.
%In MPC compilers a vectorized operation that computing M operations "at once" costs
%essentially the same ($\alpha$ or $\beta$) as an individual operation.
We elaborate on the cost model in Section~\secref{sec:model} but for now consider that
each operation has a \emph{fixed} portion (does benefits from amortization) and
a \emph{variable} portion (does not benefit from amortization): $\alpha = \alpha_\mathit{fix} + \alpha_\mathit{var}$.
This gives rise to the following formula for amortized cost: $f(n) = \alpha_\mathit{fix} + n\alpha_\mathit{var}$,
as opposed to unamortized cost $g(n) = n\alpha_\mathit{fix} + n\alpha_\mathit{var}$. We extend the same reasoning to
$\beta$-instructions.

Thus, the fixed cost of the vectorized program amounts to
$2\alpha_\mathit{fix}$ + $D \beta_\mathit{fix} + N(3\alpha_\mathit{fix})$. (The variable cost is the same in both the vectorized and non-vectorized programs.)
The first term in the sum corresponds to the vectorized
subtraction and multiplication (lines 9-10 in (c)), the second term corresponds to the for-loop on $j$ (lines 12-16) and the third
one corresponds to the remaining for-loops on $i$ (lines 19-25). 
Clearly, $2\alpha_\mathit{fix} + D\beta_\mathit{fix} + N(3\alpha_\mathit{fix}) << ND(2\alpha_\mathit{fix}+\beta_\mathit{fix}) + N3\alpha_\mathit{fix}$.
Empirically, we observe that (1) $\alpha_\mathit{var} \approx 0$ and (2) there is orders of magnitude improvement in running time and memory. 
E.g., we see about 12x improvement in online time in GMW for $N=128$. Additionally, the non-vectorized version runs out of memory for $N=256$, 
while the vectorized one runs with the standard maximal input size $N=4,096$.
%\ana{Edit numbers with final experiments.}

### 2022-05-02 overleaf/paper_SIMD.tex
Edits to shorten.

In this work, we formalize the MPC Source intermediate language and advance the idea of what we call backend-independent optimizations, in a close analogy to machine-independent optimizations in the classical compiler.  We present a compiler framework that takes a Python-like routine and produces MOTION code. We focus on a specific backend-independent optimization: novel SIMD-vectorization on MPC Source, which we show leads to significant speedup in circuit generation time and running time, as well as significant reduction in communication and number of gates over the corresponding iterative schedule.
%Our results emphasize the importance of backend-independent optimizations --- vectorization (this work) and protocol mixing (previous work) are two optimizations available at the level of MPC Source. We envision future work on backend-independent optimization: new MPC optimizations and combinations of optimizations in the vein of the classical compiler.

>>>>

In this work, we formalize the MPC Source intermediate language and advance what we call \emph{backend-independent} optimizations, in a close analogy to machine-independent optimizations in the classical compiler.  We present a compiler framework that takes a Python-like routine and produces MOTION code. We focus on a specific backend-independent optimization: novel SIMD-vectorization on MPC Source, which we show leads to significant improvement in circuit generation time, running time, and communication over the corresponding iterative schedule.
%Our results emphasize the importance of backend-independent optimizations --- vectorization (this work) and protocol mixing (previous work) are two optimizations available at the level of MPC Source. We envision future work on backend-independent optimization: new MPC optimizations and combinations of optimizations in the vein of the classical compiler.

### 2022-05-02 overleaf/prob_stmt_np_hardness.tex
Edits to shorten.

As mentioned earlier, at the lowest level, we have two types of MPC instructions (also called \emph{gates} in similar works) 1) local/non-interactive instruction (i.e. an addition instruction $A$) and 2) remote/interactive instruction (i.e. a multiplication instruction $M$). %Each instruction in the program is either an $A$-instruction or an $M$-instruction.

@@

\begin{enumerate}
    \item All $P_i$'s consist of MPC instructions of the same kind, e.g., all MUL, MUX, ADD, etc. 
    \item Def-use dependencies of the graph $G(V, E)$ should be preserved i.e. if instructions $S_i, S_j, i < j$ form a def-use i.e. an edge exists from $S_i$ to $S_j$ in $G$, then they can only be mapped to $P_{i'}, P_{j'}$ such that $i' < j'$.
\end{enumerate}

@@

where $L_\alpha$ is the number of $\alpha$-instructions and $L_\beta$ is the number of $\beta$ ones.
(We used this formula to compute the cost of the unrolled MPC Source program in~\secref{sec:overview}.)
%$cost(S_i) = \alpha$ or $\beta$. if $S_i$ is an $A$-instruction and $cost(S_i) = \beta$ if $S_i$ is an $M$-instruction. 
The cost of schedule $P$ is more interesting:

@@

The problem of finding a schedule $P$ with a minimal $cost(P)$ is shown to be NP-Hard problem, as it can be reduced to the problem of finding a \emph{shortest common supersequence}, a known NP-Hard problem\cite{Maier1978, Vazirani2010}. The shortest common supersequence problem is as follows: {\it given two or more sequences find the the shortest sequence that contains all of the original sequences.} This can be solved in $O(n^k)$ time, where $n$ is the cardinality of the longest sequence and $k$ is the number of sequences. %For our problem $n$ is the maximum length of a sequence and $k$ is the number of instructions of sequences. 
We can immediately see that the optimal schedule is the shortest schedule, since the shortest schedule minimizes the fixed cost while the variable cost remains the same.

>>>>

As mentioned earlier, at the lowest level, we have two types of MPC instructions (also called \emph{gates} or \emph{operations} in similar works) 1) local/non-interactive (e.g., an addition instruction $A$) and 2) remote/interactive (e.g., a multiplication instruction $M$). %Each instruction in the program is either an $A$-instruction or an $M$-instruction.

@@

\begin{enumerate}
    \item All $P_i$'s consist of MPC instructions of the same kind, e.g., all MUL, MUX, ADD, etc. 
    \item Def-use dependencies of the graph $G(V, E)$ are preserved i.e. if instructions $S_i, S_j, i < j$ form a def-use i.e. an edge exists from $S_i$ to $S_j$ in $G$, then they can only be mapped to $P_{i'}, P_{j'}$ such that $i' < j'$.
\end{enumerate}

@@

where $L_\alpha$ is the number of $\alpha$-instructions and $L_\beta$ is the number of $\beta$ ones.
(We used this formula to compute the cost of the unrolled MPC Source program in~\secref{sec:overview}.)
%$cost(S_i) = \alpha$ or $\beta$. if $S_i$ is an $A$-instruction and $cost(S_i) = \beta$ if $S_i$ is an $M$-instruction. 
The cost of $P$ is more interesting:

@@

%The problem of finding a schedule $P$ with a minimal $cost(P)$ is shown to be NP-Hard problem, as it can be reduced to the problem of finding a \emph{shortest common supersequence}, a known NP-Hard problem~\cite{Vazirani:2010}. 
The shortest common supersequence problem~\cite{Vazirani:2010} is as follows: {\it given two or more sequences find the the shortest sequence that contains all of the original sequences.} This can be solved in $O(n^k)$ time, where $n$ is the cardinality of the longest sequence and $k$ is the number of sequences. %For our problem $n$ is the maximum length of a sequence and $k$ is the number of instructions of sequences. 
We can see that the optimal schedule is the shortest schedule, since the shortest schedule minimizes the fixed cost while the variable cost remains the same.
